Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-01-20 awipev-CO2.Rmd
update SNAPO graph

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = at - lag(at),
                 ct_diff = ct - lag(ct))

pdelta_at_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
labs(title= "AT", x="Time", y="Delta between TA replicates")+
    Mytheme()
pdelta_ct_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
  labs(title= "CT",x="Time", y="Delta between CT replicates")+
    Mytheme()

@@

# to create periods according to SNAPCO analysis 
snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

>>>>

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

pdelta_at_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
labs(title= "AT", x="Time", y="Delta between TA replicates")+
    Mytheme()
pdelta_ct_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
  labs(title= "CT",x="Time", y="Delta between CT replicates")+
    Mytheme()

@@

# to create periods according to SNAPCO analysis 
snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00","2019-08-31 23:59:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
